The algorithm is based on the two core concepts of Voltage sensitivity analysis and Electrical distance calculation. Also, singular value decomposition is used to perform pseudo inverse of the sparse matrices. These concepts are explained in detail in this section.

\subsection{Voltage Sensitivity Analysis} \label{vsa}
The aim of the voltage sensitivity analysis is to determine the effect on the voltage of a certain node due to reactive power injection at different nodes in the feeder. Equation (\ref{eq.Pf_equation}) represents the system power-flow equation.  Here ${\Delta Q}, {\Delta P}, {\Delta |V|}$ and ${\Delta \delta}$ represent the change in real power, reactive power, voltage magnitude and voltage angle of nodes. $J$ represents the system Jacobian matrix. The elements of $J$ are shown in (\ref{eq.J_equation}).
\begin{equation}\label{eq.Pf_equation}
\begin{bmatrix}
{\Delta P}\\ {\Delta Q}
\end{bmatrix} =J\begin{bmatrix}
{\Delta|V|} \\ {\Delta\delta}
\end{bmatrix}
\end{equation}  
Where,
\begin{equation}\label{eq.J_equation}
    J = \begin{bmatrix}
{J_{P|V|}} & {J_{P\delta}}\\ {J_{Q|V|}} & {J_{Q\delta}}
\end{bmatrix}
\end{equation}

Using the components of the system Jacobian matrix the $J_{VQ}$ and $J_{VP}$ matrices can be formulated using (\ref{eq.JVQ}) and (\ref{eq.JVP}).
\begin{equation}\label{eq.JVQ}
    {J_{VQ}} = {J_{Q|V|}}-{J_{Q\delta}}{J_{P\delta}}^{-1}{J_{P|V|}}
\end{equation}

\begin{equation}\label{eq.JVP}
    {J_{VP}}={J_{P|V|}}-{J_{P\delta}}{J_{Q\delta}}^{-1}{J_{Q|V|}}
\end{equation}

Using (\ref{eq.JVQ}) and (\ref{eq.JVP}) the total voltage sensitivity due to real and reactive power injected by a DG can be calculated using (\ref{eq.V_PQ}) \cite{Th_ali}.
\begin{equation}\label{eq.V_PQ}
[\Delta|V|_{PQ}] ={ J_{VP}}^{-1} [P_{PV}]+{ J_{VQ}}^{-1} [Q_{PV}]
\end{equation}
Here, $[\Delta|V|_{PQ}], [P_{PV}] $ and $[Q_{PV}]$ represent the total voltage change, real power injected by DG and reactive power injected by DG, respectively.
Using the relation $[P_{PV}] = \frac{[Q_{PV}]}{\cos^{-1}(p.f)}$, equation (\ref{eq.V_PQ}) can be written as
\begin{equation}\label{eq.V_Q}
 [\Delta|V|_{PQ}] ={ J_{VP}}^{-1}\frac{[Q_{PV}]}{\cos^{-1}(p.f)} +{ J_{VQ}}^{-1} [Q_{PV}]
\end{equation}
From (\ref{eq.V_Q}) we can get
\begin{equation}\label{eq.Q_V}
 [\Delta|V|_{PQ}] =( \frac{J_{VP}^{-1}}{\cos^{-1}(p.f)} +{ J_{VQ}}^{-1}) [Q_{PV}]
\end{equation}
And finally from (\ref{eq.Q_V}) we can get
\begin{equation}\label{eq.PV_Q}
 [Q_{PV}] = J_{PVQ} [\Delta|V|_{PQ}] 
\end{equation}
where,
\begin{equation}
J_{PVQ} = ( \frac{J_{VP}^{-1}}{\cos^{-1}(p.f)} +{ J_{VQ}}^{-1})^{-1}
\end{equation}
 Equation (\ref{eq.PV_Q}) gives us the relation between total voltage sensitivity and reactive power injection. Here, '$p.f$' represents power factor.

\subsection{Electrical Distance Calculation}\label{edc}
Electrical distance determines the relative impact on one node due to a change in another node. The electrical distances are calculated by determining $M_{sVQ}$ according to equation (\ref{MsQV}) \cite{int1}.

\begin{equation}\label{MsQV}
\begin{bmatrix}
M_{s\alpha}P & M_{s\alpha}Q \\ 
M_{sVP} & M_{sVQ} 
\end{bmatrix} = J^{-1}
\end{equation}
 Here, $J$ is the system jacobian matrix and $M_{s\alpha}P, M_{s\alpha}Q, M_{sVP}$ and $M_{sVQ}$  are the four elements of the inverse of the system jacobian matrix. Equation (\ref{MsVq_expan}) shows the elements of $M_{sVQ}$. \cite{int1}

\begin{equation}\label{MsVq_expan}
M_{sVQ} =
\begin{bmatrix}
\frac{\delta V_{s1}}{\delta Q_{s1}}  & \frac{\delta V_{s1}}{\delta Q_{s2}} & \cdots & \frac{\delta V_{s1}}{\delta Q_{sn}}\\

\frac{\delta V_{s2}}{\delta Q_{s1}}  & \frac{\delta V_{s2}}{\delta Q_{s2}} & \cdots & \frac{\delta V_{s2}}{\delta Q_{sn}}\\

\vdots & \vdots & \vdots & \vdots\\

\frac{\delta V_{sn}}{\delta Q_{s1}}  & \frac{\delta V_{sn}}{\delta Q_{s2}} & \cdots & \frac{\delta V_{sn}}{\delta Q_{sn}}\\ 
\end{bmatrix}
\end{equation}
 
Here $V_{sn}$ and $Q_{sn}$ represent the voltage and reactive power of the node $n$. The electrical distance $D_{sij}$ between the nodes $i$ and $j$ can be calculated using (\ref{ED}) \cite{int1}. 

\begin{equation}\label{ED}
D_{sij} = -\log (\mu_{sij} * \mu_{sji})
\end{equation}

Where,
\begin{equation}
\mu_{sij} =  \frac{\delta V_{si}}{\delta Q_{sj}} / \frac{\delta V_{sj}}{\delta Q_{sj}}
\end{equation}


\subsection{Singular value decomposition and pseudo inverse}\label{svd}
\input{_pinv.tex}

% \subsection{Present Control Algorithm}
% The main objective of the coordinated voltage control algorithm is the monitoring and control of the voltage at each node of the system, by using inverter-based reactive power and voltage control with traditional voltage regulation devices in order to keep the voltages between the range desired. The calculation of the reactive power needed to be injected is obtained by using the voltage sensitivity analysis. Then electrical distance calculation is performed to choose the best node to supply reactive power. The following are the main steps of the algorithm developed.

% \input{_CVC_STEPS.tex}

% As can be seen from the steps mentioned the algorithm assumes that the real reactive power data and voltage angle and magnitude data from all nodes are available. This is not a practical consideration as installing the measurement devices at each node to collect the required data will be very costly. That is why the power flow and bad data detection steps are planned to be added to the algorithm.

